\documentclass[11pt]{article}
\usepackage{geometry}
\usepackage{comment}
\usepackage{titlesec}
\geometry{margin=0.75in,vmargin=0.75in,nohead,nofoot}
\pagestyle{empty}

\title{John M. Flinchbaugh}
\titleformat
{\section}
[display]
{\bfseries}
{\thesection}
{}
{}
\titlespacing{\section}{1.25pc}{0.5pc}{0.5pc}

\begin{document}
\fontfamily{cmss}\selectfont

\centerline{\textbf{\large John M. Flinchbaugh}}

john@hjsoft.com
\hfill
Lancaster, PA, USA
\hfill
github.com/jflinchbaugh

\hrulefill

\section*{EXPERIENCE}
\begin{itemize}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}

\item \textbf{Many Clojure Projects on GitHub},
  2018--current.
  Personal.
  \begin{itemize}
    \item Back-end, front-end, mobile, CLI, static content.
    \item https://github.com/jflinchbaugh?tab=repositories\&language=clojure
  \end{itemize}

\item \textbf{Senior Data Engineer},
  April 2019--August 2025.
  Sonatype.
  Remote.
  \begin{itemize}
    \item Maintained
      data pipelines
      and support tools used by researchers
      for cataloging
      open source libraries
      across multiple ecosystems
      using AWS, Databricks, Spark, Java, Python, Scala, and Clojure.
    \item Extensively reviewed others' code
      for correctness, quality, and future maintainability.
    \item Upgraded, and maintained software dependencies
      to remediate security vulnerabilities.
    \item Packaged applications for deployment by consumers
      with Docker, Podman, Helm, Kubernetes.
    \item Reviewed, tested, and built integration features
      for many development and deployment platforms:
      Java, Groovy, Javascript, Typescript, Jenkins, Azure DevOps.
    \item Certified Scrum Master for my team and others.
  \end{itemize}

\item \textbf{Contract Software Engineer},
    November 2014--January 2019.
    e\&e Consulting Services / PennState Hershey Medical Center.
    Hershey, PA.
\begin{itemize}
  \item Served as Scrum Master
    to transition teams to Agile/Scrum
    using JIRA.
  \item Introduced automated testing
    using Spock, Geb, Webdriver, Gradle, and Jenkins
    for building and testing web applications
    and command-line tools.
  \item Mentored on test-driven development (TDD)
    and functional programming in Groovy.
  \item Replaced legacy Java applications
    with a modern Grails, Groovy, and Javascript.
\end{itemize}

\item \textbf{Software Engineer},
    May 2012--October 2014.
    Learning Sciences International,
    Mount Joy, PA.
\begin{itemize}
  \item Introduced automated testing
    and test-driven development (TDD)
    for web application based
    on Grails, Spock, Geb, Webdriver, Bamboo, and Jenkins.
  \item Built load tests for web applications
    with JMeter and custom Geb/Webdriver scripts.
  \item Built a data warehouse on PostgreSQL
    with ETL from MongoDB for reporting with Pentaho
    and custom solutions.
\end{itemize}

\item \textbf{QA Automation Engineer},
July 2010--May 2012.
eBay Enterprise / GSI Commerce,
King of Prussia, PA.
\begin{itemize}
  \item Built functional tests for browser automation in Java, TestNG,
    Selenium WebDriver, Groovy, and Geb to test mobile e-commerce web
    applications (for smart phone, feature phone, and keitai).
  \item Refactored and enhanced existing functional test frameworks
    for streamlining test development
    and to support testing desktop and mobile web applications.
  \item Supported an agile team doing mobile web development
    as a full-time integrated team member.
\end{itemize}

\item \textbf{Senior Software Engineer},
July 2007--May 2010.
AOL MapQuest, Lancaster, PA.
\begin{itemize}
  \item Introduced and supported continuous integration,
    unit testing (JUnit),
    test coverage (Cobertura), performance metrics (JMeter),
    and code review
    for quicker, more reliable development and deployment.
  \item Worked closely with QA team members to build
    automated test tools based on Fitnesse and Groovy.
  \item Developed an ETL system
    for merging and loading data
    into search engines
    using Bash, Java, Ruby, Groovy, JPA, Hibernate, and MySQL.
\end{itemize}

\item \textbf{Java Programmer},
February 2003--July 2007.
Administrative Offices of Pennsylvania Courts,
Mechanicsburg, PA.

\begin{itemize}
  \item Redesigned and extended the Java EE middleware for the
    court management system.
  \item Increased long-term maintainability through refactoring into
    frameworks and introducing a common build system.
  \item Trained and mentored team members on new frameworks and unit testing.
\end{itemize}

\item \textbf{Senior Programmer/Analyst},
May 2000--February 2003.
Educators Mutual Life \& IBSi,
Lancaster, PA.

\begin{itemize}
  \item Designed and built a CRM portal for insurance brokers based on
    Java EE.
  \item Built a desktop application using Java, Swing, and DB2.
  \item Trained team members in Java EE, object-oriented design,
    and source control.
\end{itemize}

\item \textbf{Student Unix Administrator and Network Analyst},
March 1997--May 2000.
Millersville University,
Millersville, PA.

\begin{itemize}
  \item Maintained Solaris, HP-UX, and Linux workstations and servers.
  \item Installed network hardware and built monitoring tools.
\end{itemize}
\end{itemize}

\section*{EDUCATION}
\begin{itemize}
\item \textbf{Scrum Alliance}.
Certified Scrum Master.
2022--current.

\item \textbf{Millersville University}.
Bachelor of Science in Computer Science.
May 2000.

\item \textbf{Publications}

  \begin{itemize}
  \item Ross, Paul,
    R. Webster,
    T. Bailey,
    S. Conrad,
    M. Fiorill,
J. Flinchbaugh,
E. Velkly,
``Controlling a Pepsi Vending Machine
over the World Wide Web Using Java,''
\emph{Proceedings of the International AACE WebNet98 Conference},
Orlando, Florida, November 7--12, 1998.

\item Webster, Roger,
P. Ross,
T. Bailey,
S. Conrad,
M. Fiorill,
J. Flinchbaugh,
E. Velkly,
``Controlling a Java Enabled Pepsi Vending Machine
over the World Wide Web'',
\emph{Proceedings of the 25th Annual Conference
of the IEEE Industrial Electronics Society IECON '99 Conference},
San Jose, California,
November 30--Dec. 4, 1999,
Vol. 1, pps. 86--90.
\end{itemize}
\end{itemize}

\end{document}
